Hydra Battles and Cie

### 2021-07-21 doc/chapter-primrec.tex
more snippets

\vspace{4pt}
\noindent
\emph{From \href{../theories/html/hydras.MoreAck.PrimRecExamples.html}{MoreAck.PrimRecExamples}.}
\begin{Coqsrc}
Example Ex1 : evalPrimRec 0 zeroFunc = 0.
Proof. reflexivity. Qed.

Example Ex2 a : evalPrimRec 1 succFunc a = S a.
Proof. reflexivity. Qed.

Example Ex3 a b c d e f: forall (H: 2 < 6),
    evalPrimRec 6
                (projFunc 6 2 H) a b c d e f = d.
Proof. reflexivity. Qed.

Example Ex4 (x y z : PrimRec 2) (t: PrimRec 3):
  let u := composeFunc 2 3
                       (PRcons 2 _ x
                               (PRcons 2 _ y
                                       (PRcons 2 _ z
                                               (PRnil 2))))
                       t in
  let f := evalPrimRec 2 x in
  let g := evalPrimRec 2 y in
  let h := evalPrimRec 2 z in
  let i := evalPrimRec 3 t in
  let j := evalPrimRec 2 u in
  forall a b, j a b = i (f a b) (g a b) (h a b).
Proof. reflexivity. Qed.

Example Ex5 (x : PrimRec 2)(y: PrimRec 4):
  let g := evalPrimRec _ x in
  let h := evalPrimRec _ y in
  let f := evalPrimRec _ (primRecFunc _ x y) in
  forall a b,  f 0 a b = g a b.
Proof. reflexivity.   Qed.

Example Ex6 (x : PrimRec 2)(y: PrimRec 4):
  let g := evalPrimRec _ x in
  let h := evalPrimRec _ y in
  let f := evalPrimRec _ (primRecFunc _ x y) in
  forall n a b,  f (S n) a b = h n (f n a b) a b.
Proof. reflexivity.   Qed.                          
\end{Coqsrc}

@@

\label{sect:bigfac}
\begin{Coqsrc}
Example bigPR : PrimRec 1 :=
primRecFunc 0
  (composeFunc 0 1 (PRcons 0 0 zeroFunc (PRnil 0)) succFunc)
  (composeFunc 2 2
    (PRcons 2 1
      (composeFunc 2 1
         (PRcons 2 0 (projFunc 2 1 (le_n 2))
                 (PRnil 2))
         succFunc)
      (PRcons 2 0
        (composeFunc 2 1
          (PRcons 2 0
             (projFunc 2 0
                       (le_S 1 1 (le_n 1)))
             (PRnil 2))
          (projFunc 1 0 (le_n 1))) (PRnil 2)))
    (primRecFunc 1 (composeFunc 1 0 (PRnil 1) zeroFunc)
       (composeFunc 3 2
         (PRcons 3 1
            (projFunc 3 1 (le_S 2 2 (le_n 2)))
            (PRcons 3 0 (projFunc 3 0
                          (le_S 1 2
                                (le_S 1 1 (le_n 1))))
                    (PRnil 3)))
         (primRecFunc 1 (projFunc 1 0 (le_n 1))
                      (composeFunc 3 1
                          (PRcons 3 0
                                  (projFunc 3 1 (le_S 2 2 (le_n 2)))
                                  (PRnil 3))
                          succFunc))))). 
\end{Coqsrc}

@@

\begin{Coqsrc}
Example  mystery_fun : nat -> nat := evalPrimRec 1 bigPR.

Compute map mystery_fun[0;1;2;3;4;5;6] : t nat _.
\end{Coqsrc}

\begin{Coqanswer}
 = 1 :: 1 :: 2 :: 6 :: 24 :: 120 :: 720 :: nil
     : t nat 7
\end{Coqanswer}

>>>>

\vspace{4pt}
\noindent
\emph{From \href{../theories/html/hydras.MoreAck.PrimRecExamples.html}{MoreAck.PrimRecExamples}.}

\input{movies/snippets/PrimRecExamples/evalPrimRecEx}

@@

\label{sect:bigfac}

\input{movies/snippets/PrimRecExamples/bigPRa}

@@

\input{movies/snippets/PrimRecExamples/bigPRb}
